Assessing MCR Discussion Usefulness using Semantic Similarity

### 2014-07-30 sections/background.tex
working on section 3
more refactorings
working on result RQ1

An overview of MCR process based on Gerrit system is shown in Fig. \ref{fig:process}.
The grey area shows the review process of the system which composed of four main steps:
(1) an author creates a patch and submits a set of new or modified files as a review request to Gerrit system.
(2) reviewers examine the proposed code changes for defects or concerns.
(3) reviewers provide comments to the author. The author creates a revised proposed change according to the comments and re-submits for review. Then, reviewers will examine the revised proposed change. If the revision is not approved, reviewers provide comments to fix and the process continues until (4) reviewers can determine that a proposed change can be merged into the project (approved change) or should not be merged (reject the change).

@@

According to this process, reviewers' comments are the most important factor in determining software quality.
In particular, McIntosh et. al. \cite{Mcintosh} found that components which were reviewed without discussion are likely to contain bugs.
However, tools supporting MCR allow reviewers to freely write messages to the author (and other reviewers), and frequently, these comments are superficial or do not clearly identify defects or relevant issues for the proposed change and are thus of questionable usefulness.

% (e.g. coding styles, documentation, process workflow, etc.)

For example, a comment may be related to something outside the scope of the proposed change, perhaps personal issues or inter-personal communication (e.g. ``Keep up the good work!").
Microsoft developers reported that the reviewers often only focus on minor logic errors rather than discussing deeper design\cite{Bacchelli2013a} issues.
Our observations of the Qt project also correspond to this finding.
We found some comments are superficial and unhelpful to the proposed changes.
For example, the superficial and unconfident comment shown in Fig. \ref{fig:example}(a) is indeed within the scope of the proposed change yet provides little useful information,
while the comment in Fig. \ref{fig:example}(b) about using the version control system (in this case Git) is clearly out of scope and not directly useful for the proposed change.

>>>>

An overview of MCR process based on Gerrit system is shown in Fig. \ref{fig:process}.
The grey area shows the review process of the system which composed of four main steps:
(1) an author creates a patch and submits a set of new or modified files as a review request to Gerrit system.
(2) reviewers examine the proposed code changes for defects or concerns.
(3) reviewers provide comments to the author.
The author creates a revised proposed change according to the comments and re-submits for review.
Then, reviewers will examine the revised proposed change.
If the revision is not approved, reviewers provide comments to fix and the process continues until
(4) reviewers can determine that a proposed change can be merged into the project (approved change) or should not be merged (rejected).

According to this process, reviewers' comments are the most important factor in determining software quality.
In particular, McIntosh et. al. \cite{Mcintosh} found that components which were reviewed without discussion are likely to contain bugs.
However, tools supporting MCR allow reviewers to freely write messages to the author (and other reviewers), and frequently, these comments are superficial or do not clearly identify defects or relevant issues for the proposed change and are thus of questionable usefulness.
% (e.g. coding styles, documentation, process workflow, etc.)
For example, a comment may be related to something outside the scope of the proposed change, perhaps personal issues or inter-personal communication (e.g. ``Keep up the good work!").
Microsoft developers reported that the reviewers often only focus on minor logic errors rather than discussing deeper design\cite{Bacchelli2013a} issues.
Our observations of the Qt project also correspond to this finding.
We found that some comments are superficial and unhelpful to the proposed changes.
For example, the superficial and unconfident comment shown in Fig. \ref{fig:example}(a) is indeed within the scope of the proposed change yet provides little useful information,
while the comment in Fig. \ref{fig:example}(b) about using the version control system (in this case Git) is clearly out of scope and not directly useful for the proposed change.

@@

### 2014-07-30 sections/introduction.tex
add conclusion

Because performance of code review has a clear relationship to the quality of the software, many studies have investigated factors that influence MCR\cite{Baysal2001,Mcintosh,Beller,Hamasaki2013}.
However, little research exists investigating how review discussion for a proposed change impacts software quality.
Given that most proposed changes are triggered from reviewer comments \cite{Beller}, 
it is possible that they can either positively contribute to the proposed changes (i.e. are ``\emph{useful}''), or be a discussion which contributes little directly to the proposed changes (i.e. relatively ``\emph{useless}'' ). 
Since MCR does not require strict guidelines, checklists, or formal processes, some reviewers tend to look for trivial issues (e.g. coding styles), leaving deeper issues undiscussed \cite{Bacchelli2013a}.
%This is a concern because a high-degree of useless comments not only fails to contribute to improving quality, but also degrades the cost-effectiveness and perceived utility of MCR.
This is a concern because a low-degree of useful comments can degrade the overall quality and perceived utility of MCR.

Prior research has focused mostly on the relation between number of comments and quality.
To the best of our knowledge, the connection between degree of useful and useless comments and quality has not been studied.
One reason for this may be that to assess the impact of discussion in MCR, effort intensive manual classification is required as in the study of Beller et. al. \cite{Beller}.
MCR can produce a massive amounts of changes requests and comments\cite{Balachandran2013,Thongtanunam2014} and it is painstaking and time consuming to classify comments usefulness.
Moreover, the comments in MCR are unstructured natural text, open to subjective judgment, tacit understanding, and possible mis-interpretation.

@@

In this paper, we present a text mining approach using semantic similarity to assist in classifying the usefulness of comments.
The proposed approach is meant to better enable classifying large amounts of MRC comments in order to conduct comment and code quality studies, such as those discussed earlier, as manual classification can quickly become an untenable task.
By introducing automation support based on objective empirical criteria,
our proposed method aims to both reduce effort and increase confidence in classification to a degree that is practical for addressing very large MRC data sets.
%Because usefulness of a comment is not precisely defined and is a subjective qualification, we cannot, and do not intend to fully automate or replace human driven classification.  
Through a case study of Qt project, we address the following research questions:
\begin{ResearchQuestions}
\item[RQ1:] Is semantic similarity a good indicator of MCR comment usefulness?\\
\item[RQ2:] Is semantic similarity classification cost-efficient, assurable, and scalable?
\end{ResearchQuestions}

@@

%We create our predictive model by estimating pairs of similarity and dissimilarity values that best discriminate between useful and useless comments.
%This is accomplished by optimizing for prediction performance measures such as Precision and Recall, through F-measure.
%
%For our case study of the method, we used a review history from the Gerrit\footnote{\url{https://code.google.com/p/gerrit/}} system from Qt\footnote{\url{http://qt-project.org/}}, an open source project for a cross-platform application and UI framework supported by Digia corporation.
%For training and validation of our approach, three experts manually classified the usefulness for 320 comments.
%We also apply our predictive model to the full set of 17,000 \dan{what's the actual number?}
%comments to obtain a preliminary estimate in the quality of reviews and address the following three research questions:
%
%\noindent \textbf{RQ1:} Is semantic similarity a good indicator of MCR comment usefulness?\\
%\noindent \textbf{RQ2:} Do code reviewers intensively discuss on the proposed changes?\\
%\noindent \textbf{RQ3:} Is semantic similarity classification cost-efficient, assurable, and scalable?
%
%\noindent In addition to addressing the research questions above, the main contributions of this paper are:
%\dan{these are more "results" than contributions.... need to reword this!}
%\begin{itemize}
%\item A practical approach to mine natural text of comments in code reviews and classify their usefulness based on VSM similarity.
%\item The experimental results, which show that the approach can classify comments with an F$_1$ score of 0.681 and 0.693.
%\item We found that 85\% of comments in Gerrit are automatically generated and not likely useful (but important for record keeping). For the remaining 15\%, about 43\% of them are automatically classified as useful, while about 34\% are classified as not useful. The remaining 23\% are undetermined and require manual classification. Thus the classification effort is reduced by about 77\%.
%\item \TODO{xx}\% of the comments did not have unanimity (i.e. unclear), and of these \TODO{yy}\% were automatically determined to be useful or not useful. Follow up with dissenting assessors found mis-judgement occurred \TODO{zz}\% of the time whereby in retrospect the comment would have had unanimity. This indicates the method is useful in identifying subjective judgement errors. 
%\item Of the 23\% not automatically classified (i.e. undetermined), \TODO{qq}\% were unclear. Of the \TODO{(1-qq)}\% with unanimity, followup with assessors found in retrospect they would change their assessment making the comment unclear. This indicates the method is useful in identifying chance unanimity errors or group think bias.
%\end{itemize} 
%%%%%%%%%%%%%%%%%%%%%%%%%%%

>>>>

Because performance of code review has a clear relationship to the quality of the software, many studies have investigated factors that influence MCR\cite{Baysal2001,Mcintosh,Beller,Hamasaki2013}.
However, little research exists investigating how review discussion for a proposed change impacts software quality.
Given that most proposed changes are triggered from reviewer comments \cite{Beller}, 
it is possible that they can either positively contribute to the proposed changes (i.e. are ``\emph{useful}''), or be a discussion which contributes little directly to the proposed changes (i.e. relatively ``\emph{useless}''). 
Since MCR does not require strict guidelines, checklists, or formal processes, some reviewers tend to look for trivial issues (e.g. coding styles), leaving deeper issues undiscussed \cite{Bacchelli2013a}.
%This is a concern because a high-degree of useless comments not only fails to contribute to improving quality, but also degrades the cost-effectiveness and perceived utility of MCR.
This is a concern because a low-degree of useful comments can degrade the overall quality and perceived utility of MCR.

Prior research has focused mostly on the relation between number of comments and quality.
To the best of our knowledge, the connection between degree of useful and useless comments and quality has not been studied.
One reason for this may be that to assess the impact of discussion in MCR, effort-intensive manual classification is required as in the study of Beller et. al. \cite{Beller}.
MCR can produce a massive amounts of changes requests and comments\cite{Balachandran2013,Thongtanunam2014} and it is painstaking and time consuming to classify their usefulness.
Moreover, comments in MCR are unstructured natural text, open to subjective judgment, tacit understanding, and possible misinterpretation.

@@

In this paper, we present a text mining approach using semantic similarity to assist in classifying the usefulness of comments.
The proposed approach is meant to ease classifying large amounts of MRC comments in order to conduct comment and code quality studies (such as those discussed earlier) as manual classification can quickly become an untenable task.
By introducing automation support based on objective empirical criteria, our proposed method aims to both reduce effort and increase confidence in classification to a degree that is practical for addressing very large MRC data sets.
%Because usefulness of a comment is not precisely defined and is a subjective qualification, we cannot, and do not intend to fully automate or replace human driven classification.  
Through a case study of Qt project, we address the following research questions:
\begin{ResearchQuestions}
\item[RQ1:] Is semantic similarity a good indicator of MCR comment usefulness?\\
\item[RQ2:] Is semantic similarity classification cost-efficient, assurable, and scalable?
\end{ResearchQuestions}

@@

%We create our predictive model by estimating pairs of similarity and dissimilarity values that best discriminate between useful and useless comments.
%This is accomplished by optimizing for prediction performance measures such as Precision and Recall, through F-measure.
%
%For our case study of the method, we used a review history from the Gerrit\footnote{\url{https://code.google.com/p/gerrit/}} system from Qt\footnote{\url{http://qt-project.org/}}, an open source project for a cross-platform application and UI framework supported by Digia corporation.
%For training and validation of our approach, three experts manually classified the usefulness for 320 comments.
%We also apply our predictive model to the full set of 17,000 \dan{what's the actual number?}
%comments to obtain a preliminary estimate in the quality of reviews and address the following three research questions:
%
%\noindent \textbf{RQ1:} Is semantic similarity a good indicator of MCR comment usefulness?\\
%\noindent \textbf{RQ2:} Do code reviewers intensively discuss on the proposed changes?\\
%\noindent \textbf{RQ3:} Is semantic similarity classification cost-efficient, assurable, and scalable?
%
%\noindent In addition to addressing the research questions above, the main contributions of this paper are:
%\dan{these are more "results" than contributions.... need to reword this!}
%\begin{itemize}
%\item A practical approach to mine natural text of comments in code reviews and classify their usefulness based on VSM similarity.
%\item The experimental results, which show that the approach can classify comments with an F$_1$ score of 0.681 and 0.693.
%\item 
%\item \TODO{xx}\% of the comments did not have unanimity (i.e. unclear), and of these \TODO{yy}\% were automatically determined to be useful or not useful. Follow up with dissenting assessors found mis-judgement occurred \TODO{zz}\% of the time whereby in retrospect the comment would have had unanimity. This indicates the method is useful in identifying subjective judgement errors. 
%\item Of the 23\% not automatically classified (i.e. undetermined), \TODO{qq}\% were unclear. Of the \TODO{(1-qq)}\% with unanimity, followup with assessors found in retrospect they would change their assessment making the comment unclear. This indicates the method is useful in identifying chance unanimity errors or group think bias.
%\end{itemize} 
%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2014-07-30 sections/results.tex

To determine similarity and dissimilarity thresholds for useful and useless model, we iterated $s_t$ and $d_t$ values from every unique similarity and dissimilarity values in our data set.
%Table \ref{tb:thresholds} shows 5 sets of thresholds that best classify useful and useless comments based on F$_1$ score.
We selected the thresholds that best classify useful and useless comments based on F-measure score and applied models, i.e. useful: $\Theta(c,S_T=0.015529,D_T=2.494944)$ and useless: $\Omega(c,S_T=0.087522,D_T=2.265679)$ on the samples.

@@

There is an overlap section as shown in Fig. \ref{fig:scatter}. This is a conflict results between our two models where a comment received true outcome from both classification models.  
This is phenomenon can occur since similarity and dissimilarity values of each group are vague and both  models tend to maximize coverage of classification. However, from the results in Table \ref{tb:classify_number}, only three comments were selected by both models (overlap). This is very small error for our models. Excluding the overlap classification result, we can calculate precision and recall as described in Table \ref{tb:classify_number}. Furthermore, there are 12 useless comments (14\%) and 21 useful comments (17\%) still are undetermined (drawn in white area). These comments were not satisfied our models. This suggests us that other indicators are needed to satisfy condition and identify usefulness.
%From the example comment, it shows that these comments discussed on \TODO{insert topic}, but did not contain any word in common.

@@

\caption{Number of comments classified by our approach against ground truth data}
\begin{tabular}{cccccc}
\hline
Result from & \multicolumn{4}{c}{Results from manual assessment}  & \multirow{3}{*}{Precision}\\ \cline{2-5}
Classification &  Useless  & Unclear  & Unclear & Useful \\
Models&  (\texttt{YES}=0) & (\texttt{YES}=1) & (\texttt{YES}=2) & (\texttt{YES}=3) \\
\hline \hline
Useful & 3 & 12 & 24 & 94 & 0.706\\
Useless & 69 & 23 & 7 & 6 &  0.657\\
Overlap & 1 & 1 & 0 & 1 & - \\
Undetermined & 12 & 24 & 20 & 21 & - \\
\hline
Recall & 0.812 & - & - & 0.770\\ \hline 
\end{tabular}
\label{tb:classify_number}
\end{table}

@@

%After we performed cross validation, we obtained the following result:
%for positive and negative classifications,
%we obtained an average F$_1$ score of 0.693 and 0.681,
%with standard deviation of 0.090 and 0.118, respectively.
%This indicates that we can use our approach to classify with confident of 69.8\%.

%After the similarity and distance metrics have been calculated,
%these metrics appear to be able to separate the useful comments from the non-useful ones,
%as can be seen in Fig.\ref{fig:scatter}.
%Note that many comments have a cosine similarity metric of 0.
%This is because the comment text and the corresponding commit message has no word in comment.

\begin{ResearchQuestions}
\item[RQ2:] Is semantic similarity classification cost-efficient, assurable, and scalable?
\end{ResearchQuestions}

To answer this question, timestamps are recorded as three people assess each comment.
Since three people work on their leisure time, there is much variability in the time between each vote.
Therefore, we ignored the time interval between two votes if they are more than 10 minutes apart.

On average, it takes 28 seconds to assess each comment.
However, the median is 10 seconds, suggesting that most comments take only a little amount of time to assess, while only few comments take long time.
This also suggests that the time to assess each comment is not normally distributed.
The standard deviation is 45 seconds.

To estimate the total time for us to assess these 318 comments,
we multiplied the average time by the number of comments and the number of people.
This results in 7.42 person hours.

However, to manually assess all 10,583 comments---even with only one person---this would take 82.3 person hours.
By running our model through all 10,583 comments, only 2,487 comments receive undetermined result.
That means that about 77\% of the effort is saved.

Applying our classification model to all comments results in the proportions shown in Table \ref{tb:percent}.
As the figure shows, the proportion is similar to the result of .

\begin{table}[!t]
\caption{Proportion of classifications when applied to the whole data set.}
\small
\centering
\def\arraystretch{1.2}
\begin{tabular}{ccccccc}
\hline
Class &        over all samples & only training data  \\ \hline
useful &            42.8\%      &      41.8\%         \\
useless &           33.7\%      &      33.1\%         \\
undetermined &      23.5\%      &      25.1\%         \\ \hline
\end{tabular}
\label{tb:percent}
\end{table}

%\pick{Note from Dan sensei,}
%For cpost effectivness we can state the reduction  percentage in the number of comments that much be checked manually.
% Also point out how much effort manual classification takes and that it is error prone (probably mor so than the automated method!
%You cannot, but some estimates are possble
%first, human beings have a fairly well known rate of making errors in classification
%second, look at the comments in the training set that the method classified differently, especially the unclear.
%Review these to see if the method suggested a better classification than was originally made by the assessors
%You can consider these errors. Now look at what wans the percent of errors in the training set
%This is also an estimate of the human error rate

>>>>

To determine similarity and dissimilarity thresholds for useful and useless model, we iterated $s_t$ and $d_t$ values from every unique similarity and dissimilarity values in our data set.
%Table \ref{tb:thresholds} shows 5 sets of thresholds that best classify useful and useless comments based on F$_1$ score.
We selected the thresholds that best classify useful and useless comments based on F-measure score and applied models.
The selected models are $\Theta(c,S_T=0.015529,D_T=2.494944)$ for useful comments, and $\Omega(c,S'_T=0.087522,D'_T=2.265679)$ for useless comments.

@@

There is an overlap section as shown in Fig. \ref{fig:scatter}. This is a conflict results between our two models where a comment received true outcome from both classification models.  
This is phenomenon can occur since similarity and dissimilarity values of each group are vague and both  models tend to maximize coverage of classification. However, from the results in Table \ref{tb:classify_number}, only three comments were selected by both models (overlap). This is very small error for our models. Excluding the overlap classification result, we can calculate precision and recall as described in Table \ref{tb:classify_number}. Furthermore, there are 12 useless comments (14\%) and 21 useful comments (17\%) still are undetermined (drawn in white area). These comments were not satisfied our models. This suggests us that other indicators are needed to investigate for usefulness classification.

%From the example comment, it shows that these comments discussed on \TODO{insert topic}, but did not contain any word in common.

@@

\caption{Number of comments classified by our approach against ground truth data}
\begin{tabular}{cccccc}
\hline
Result from & \multicolumn{4}{c}{Results from manual assessment}  & \multirow{3}{*}{Precision}\\ \cline{2-5}
Classification &  Useless  & Unclear  & Unclear & Useful \\
Models&  (\texttt{YES}=0) & (\texttt{YES}=1) & (\texttt{YES}=2) & (\texttt{YES}=3) \\
\hline \hline
Useful & 3 & 12 & 24 & 95 & 0.709\\
Useless & 69 & 23 & 7 & 6 &  0.657\\
Overlap & 1 & 1 & 0 & 1 & - \\
Undetermined & 12 & 24 & 20 & 20 & - \\
\hline
Recall & 0.812 & - & - & 0.778\\ \hline 
\end{tabular}
\label{tb:classify_number}
\end{table}

@@

%After we performed cross validation, we obtained the following result:
%for positive and negative classifications,
%we obtained an average F$_1$ score of 0.693 and 0.681,
%wit
